\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Data Analysis and Integration  \hfill May 2021 --- Present}}
\subtext{BTJN, LLC \hfill Houston, TX}
\begin{zitemize}
%    \skilling{\href{https://docs.jnapolitano.io/parts/analysis/business-analysis/project-retail-sales-forecasting/code-base/SalesForcasting.html}{Sales Forecasting}}
    \item{Modeled retail sales of 57 retail stores with SARINA, Holt-Winter, and Exponential Smoothing models with Statsmodels API to streamline inventory procedures. Detected products most likely to sell to consumers by store.  Tested effects of seasonality on consumer purchasing.}
%    \skilling{\href{https://docs.jnapolitano.io/parts/data/web-scraping/index.html}{Data Mining}}
    \item{Mined data from Rest API to generate 250,000 qualified sales leads. Clustered leads by location and volume of business to identify most valuable targets for client's marketing strategy.}
%    \skilling{Data Engineering}
%    \skilling{\href{https://docs.jnapolitano.io/_modules/csv_to_neo.html\#DataPipelineFunctions}{Data Transformation}}{Transformed results to client's data format with PySpark.}
%    \skilling{\href{https://docs.jnapolitano.io/_modules/csv_to_neo.html\#DataUploadFunctions}{Data Warehousing}}{Stored historical data in Neo4j warehouse.}
%    \skilling{\href{https://docs.jnapolitano.io/parts/data/web-scraping/general-purpose/docs/realtor_scraper_sheets_4/index.html}{Data Integration}}{Integrated data into client’s existing Google Sheets workflow.}
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Author and Research Lead  \hfill Jan 2017 --- Aug 2019}}
\subtext{University of Central Florida \hfill Orlando, Fl}
\begin{zitemize}
    %\skilling{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/analysis.html}{Inferential Analysis}}
    \item{Identified socioeconomic features correlated with increased event probability.  Examined the impact of large scale infrastructure projects and local investment on violence and social integration. Performed time-series analysis of economic integration to test whether social investment decreases terrorist activity and regional violence.}
%    \skilling{\href{https://www.degruyter.com/document/doi/10.1515/peps-2019-0036/html?lang=en}{Article Publication}}
%    \item{Published work in the Journal of Peace Economics, Peace Science and Public Policy.  Prepared accompanying presentation for peer review at the Peace Science Conference at the Hague.}
    %\skilling{\href{https://docs.jnapolitano.io/parts/analysis/political-analysis/terrorism-conflict/project-turkish-kurdish/pdf.html}{Feature Extraction}}
    \item{Standardized feature extraction and storage methodology for team of 5 research assistants.  Trained team members to collect data with SQL queries. Verified human coded data to ensure rigor for publication.}
    %\skilling{Data Integration}{Warehoused data to mongoDB.} f
%    \skilling{Data Visualization}{Visualized P.O.L.E with Matplotlib.}
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Research Assistant \hfill Jan 2017 --- Jan 2018}}
\subtext{University of Central Florida \hfill Orlando, Fl}
\begin{zitemize}
    %\skilling{Sentiment Analysis}
    \item{Automated sentiment analysis with Python NTLK to correlate behavior to perceived emotional state.  Identified likely foreign policy actions of the UK parliament.}
    %\skilling{Data Verification}
    \item{ANOVA tested human scored sentences against automated scoring to ensure validity of qualitative human scoring.}
%    \skilling{Data Management}{Standardized data aggregation and storage procedures.}
\end{zitemize}


\end{document}